---
title: "Tutorial"
#author: "Matt Galloway"
#date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEngine{knitr::knitr}
  %\usepackage[UTF-8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
```


BLAH BLAH BLAH!!!!!


<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}
library(SCPME)

#  generate data from a sparse matrix
# first compute covariance matrix
S = matrix(0.7, nrow = 5, ncol = 5)
for (i in 1:5){
  for (j in 1:5){
    S[i, j] = S[i, j]^abs(i - j)
  }
}

# print oracle precision matrix (shrinkage might be useful)
(Omega = round(qr.solve(S), 3))

# generate 100 x 5 matrix with rows drawn from iid N_p(0, S)
set.seed(123)
Z = matrix(rnorm(100*5), nrow = 100, ncol = 5)
out = eigen(S, symmetric = TRUE)
S.sqrt = out$vectors %*% diag(out$values^0.5) %*% t(out$vectors)
X = Z %*% S.sqrt

# snap shot of data
head(X)

```
<br>\vspace{0.5cm}

As described earlier in the report, the maximum likelihood estimator (MLE) for Omega is the inverse of the sample precision matrix $S^{-1} = \left[\sum_{i = 1}^{n}(X_{i} - \bar{X})(X_{i} - \bar{X})^{T}/n \right]^{-1}$:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# print inverse of sample precision matrix (perhaps a bad estimate)
round(qr.solve(cov(X)*(nrow(X) - 1)/nrow(X)), 5)


```
<br>\vspace{0.5cm}

However, because Omega (known as the *oracle*) is sparse, a shrinkage estimator will perhaps perform better than the sample estimator. Below we construct various penalized estimators:

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# elastic-net type penalty (set tolerance to 1e-8)
shrink(X, tol.abs = 1e-8, tol.rel = 1e-8)

```
<br>\vspace{0.5cm}

**LASSO:**

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# lasso penalty (default tolerance)
shrink(X, alpha = 1)


```
<br>\vspace{0.5cm}

**RIDGE:**

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# ridge penalty
shrink(X, alpha = 0)


```
<br>\newpage

This package also has the capability to provide heat maps for the cross validation errors. The more bright (white) areas of the heat map pertain to more optimal tuning parameters.

<br>\vspace{0.5cm}
```{r, message = FALSE, echo = TRUE}

# produce CV heat map for ADMMsigma
shrink = shrink(X, tol.abs = 1e-8, tol.rel = 1e-8)
plot(shrink, type = "heatmap")

```
<br>\newpage

```{r, message = FALSE, echo = TRUE}

# produce line graph for CV errors for ADMMsigma
plot(shrink, type = "line")

```
<br>\newpage
